The Socialization of Meritocracy: The role of the Family and the School

### 2023-03-06 paper-blinded.Rmd
Ajustes youth (#8)
* ajustes1

* ajustes submission Y&S

* clean papelera

* update tablas figuras preprint

author:
- name: Juan Carlos Castillo ^[Corresponding author - juancastillov@uchile.cl - http://jc-castillo.com/]
  number: 1,2
- name: Julio Iturra
  affiliation: Centro de Estudios de Conflicto y Cohesión Social
  number: 2
- name: Francisco Meneses
  affiliation: Departamento de Sociología, Universidad de Chile
  number: 1
- name: Martín Venegas
  number: 1

@@

keywords: meritocracy socialization, sense of justice, Chile

@@

@@

## Variables:

@@

df.esc<- dfSummary(select(df_n2,
                          dependencia_factor_est,
                          nse_grupo),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = 0.75,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               # col.widths = c(1000,10,10,10,10)
               )
df.esc$Variable <- NULL # delete variable column
view(df.esc,file = "desc01_esc.html") # Ver tabla en un archivo HTML
webshot(url ="desc01_esc.html" ,file ="output/tables/desc01_esc.png",vheight = 10) # Foto al documento HTML para guardar en png
file.remove(c("desc01.html","desc01_esc.html")) # Remover archivo HTML
```

@@

\begin{equation}
   \text{Sentido de justicia en notas}= ln(\frac{\text{nota obtenida}}{\text{nota justa}}) (\#eq:jef)
\end{equation}

@@

Because the sample has a hierarchical structure (students nested in schools), multilevel regressions were estimated to contrast the hypotheses following the  steps recommended to estimate and report using this type of models [@aguinis_bestpractice_2013a]. Since the two indicators of student perception of meritocracy are ordinal variables, we consideded estimations according to this type of measurement [@arfan_ordinal_2017a] [^2]. The analysis was carried out with statistical software `R` version 4.0.3 "Bunny-Wunnies Freak Out."

[^2]: In multilevel ordinal models, the dependent variable represents the calculation of the cumulative probability that a student will respond up to $C$ in the meritocracy perception indicators,  $Y_{cij}$ being an ordered categorical response of a student $i^{th}$ in a school (cluster) $j^{th}$ with $C$ ordered categories, coded as $C = 1,2,3,4$. This probability is calculated based on the intercept for each category $a_c$, the coefficients $\gamma_1$ and $\gamma_2$for the perception of meritocracy of the parents and the sense of justice in grading respectively, $\gamma_n$for the control variables, $u_{0j}$as the error term for a school $j$and $e_{ij}$as the estimation error for the individual $i$in a school $j$. The library `clmm2` of R. was used for the estimation.

@@

Multivariate Analysis

>>>>

# author:
# - name: Juan Carlos Castillo ^[Corresponding author - juancastillov@uchile.cl - http://jc-castillo.com/]
#   number: 1,2
# - name: Julio Iturra
#   affiliation: Centro de Estudios de Conflicto y Cohesión Social
#   number: 2
# - name: Francisco Meneses
#   affiliation: Departamento de Sociología, Universidad de Chile
#   number: 1
# - name: Martín Venegas
#   number: 1

@@

keywords: meritocracy perception, sense of justice, socialisation

@@

  bookdown::word_document2:
    reference_docx: input/template.docx

@@

## Variables

@@

df.esc<- dfSummary(select(df_n2,
                          dependencia_factor_est,
                          nse_grupo),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = 0.75,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               # col.widths = c(1000,10,10,10,10)
               )
df.esc$Variable <- NULL # delete variable column
view(df.esc,file = "desc01_esc.html") # Ver tabla en un archivo HTML
webshot(url ="desc01_esc.html" ,file ="output/tables/desc01_esc.png",vheight = 10) # Foto al documento HTML para guardar en png
# file.remove(c("desc01.html","desc01_esc.html")) # Remover archivo HTML
```

@@

\begin{equation}
   \text{Sense of justice in grades}= \ln\biggl(\frac{\text{grade obtained}}{\text{grade deserved}}\biggl) (\#eq:jef)
\end{equation}

@@

Because the sample has a hierarchical structure (students nested in schools), multilevel regressions were estimated to contrast the hypotheses following the steps recommended to estimate and report using this model [@aguinis_bestpractice_2013a]. Since the two indicators of student perception of meritocracy are ordinal variables, we considered estimations according to this measurement [@arfan_ordinal_2017a].

Multilevel Ordinal Logit models uses the cumulative probability of a student's responses up to $C$ in the indicator, $Y_{cij}$ of student $i^{th}$ in a school (cluster) $j^{th}$ with $C$ categories. The estimation considers an intercept for each response category, conditional to the sense of justice in students' grades, parents' meritocracy perception, and controls. The model takes into account $u_{0j}$ as the error term for a school $j$and $e_{ij}$ as the estimation error for the individual $i$in a school $j$. For the statistical computation we use the  `ordinal` [@christensen_ordinal_2019] `R` library [@rcoreteam_language_2022].

@@

## Multivariate Analysis
